Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-13 ms_pre_post.Rmd
Finish section on Evolution of polyandry to avoid inbreeding

We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained. Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g. @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015]. For example, @Pizzari2004 find that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity. Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008] most likely due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015]. Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003]. Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 5), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.  <!--- start talking abou these now --->

>>>>

We predict evolution of polyandry in populations where inbreeding depression is severe and evolution of inbreeding avoidance through post-copulatory mechanisms is not constrained. Post-copulatory mechanisms of inbreeding avoidance have been observed under these conditions in experimental systems across diverse taxa [e.g. @Pizzari2004; @Firman2008; @Bretman2009; @Gasparini2011; @Tuni2013; @Firman2015]. For example, @Pizzari2004 find that the number of sperm arriving to eggs is lower for full siblings of female red jungefowl (*Gallus gallus*) than it is for non-relatives, even after controlling for effects of order of oviposition and social familiarity. Similarly, Firman and Simmons [-@Firman2008; -@Firman2015] have shown evidence of post-copulatory inbreeding avoidance in house mice, finding fertilisation to be biased toward unrelated males independent of the order in which mating occurs [@Firman2008], perhaps due to post-copulatory mechanisms expressed through the secretion of gametic proteins originating in female's eggs [@Firman2015]. Interestingly, female house mice have also been shown to express pre-copulatory inbreeding avoidance  [@Potts1991; @Roberts2003]. Our results suggest that post-copulatory inbreeding avoidance is unlikely to evolve when females can already avoid inbreeding through pre-copulatory mechanisms (Figure 5), meaning that evolution of post-copulatory inbreeding avoidance could reasonably be hypothesised to have preceded evolution of pre-copulatory inbreeding avoidance in mice.

Specific mechanisms of post-copulatory inbreeding avoidance are difficult to identify, but recent experimental studies have shown how females can successfully bias fetilisation after mating has occurred in both vertebrates [e.g., @Gasparini2011] and invertebrates [e.g., @Tuni2013]. For example, @Gasparini2011 artificially inseminated female guppies (*Poecilia reticulata*) with equal quantities of sperm from full-siblings and unrelated males, finding that fertilisation success was higher in non-relatives because the velocity of full siblings' sperm was reduced by females' ovarian fluids. Biased fertilisation toward non-relatives might also be accomplished through selective storage of sperm. For example, in black field crickets (*Teleogryllus commodus*), females attempt to remove the spermataphores of unwanted male mates after copulation, while male mates guard females to prevent spermatophore removal [@Bussiere2006]. Even if females are unable to remove spermatophores of unwanted mates, @Tuni2013 found evidence that female *T. commodus* are capable of controlling which males' sperm is transferred to their spermatheca, most likely through physical control of the spermathical duct, and reduce sperm storage when being guarded by a related male. Our results suggest that evolution of such post-copulatory inbreeding avoidance might increase selection for polyandry, especially if pre-copulatoyr inbreeding avoidance is costly (Figure 1) or constrained (Figure 3).

Costs of polyandry and inbreeding avoidance
----------------------------------------------

Constraints on polyandry and inbreeding avoidance
----------------------------------------------

<!--- start talking abou these now --->
